\documentclass[a4paper]{ReadableCV}

\color{black}

\begin{document}

\setPageColour{white}
\setHeaderAlignment{left}
\setHeadingColours{DarkOliveGreen4}
\setContactLocation{opposite}

\setYourName{Eric Ashenden}
\setYourJobTitle{Senior Site Reliability Engineer}
\setYourMobileNo{(804) 402-3334}
\setYourHomeNo{Black Hawk, CO}
\setYourEmailAddr{eashenden93@gmail.com}
\setYourWebAddr{\href{https://ericashenden.com}{ericashenden.com}}
\setYourLinkedInAddr{\href{https://linkedin.com/in/ericashenden}{linkedin.com/in/ericashenden}}

\showHeader

\setSectionAlignment{left}

% =========================
% Personal Profile
% =========================
\newHeading{Personal Profile}

Senior Site Reliability Engineer focused on building reliable, scalable systems on modern cloud platforms. Experienced in Kubernetes, infrastructure automation, and observability, with an emphasis on reducing operational risk and improving developer experience through clear, maintainable systems.

\bigskip

% =========================
% Core Skills
% =========================
\newHeading{Core Skills}

\addSkills
{Distributed systems \& reliability engineering}
{Infrastructure as Code \& cloud automation}
{Observability, monitoring, \& incident analysis}
{CI/CD pipelines \& release automation}
{Production troubleshooting \& operational tooling}
{Technical mentorship \& cross team collaboration}
{}{}{}

\bigskip

% =========================
% Career Summary
% =========================
\newHeading{Career Summary}

\setJobCompanyOrder{JobFirst}

% -------- Senior SRE --------
\newRole{2023 -- Present}
{Senior Site Reliability Engineer}
{Corpay}

\roleAchievements
{Led reliability improvements across Kubernetes workloads, including introducing KEDA based scaling, optimizing Helm charts, and improving deployment pipelines to increase efficiency and security.}
{Drove the migration from legacy identity approaches to Kubernetes Workload Identity, reducing operational risk and simplifying service authentication.}
{Expanded observability by building custom Datadog monitors and dashboards and developing a Python based SSL certificate monitoring tool to close visibility gaps.}
{Automated operational workflows to reduce toil, debugged critical production incidents, and improved overall system resilience.}
{Mentored junior SREs through incident response, troubleshooting, and automation best practices.}
{}{}{}{}

\bigskip

% -------- SRE --------
\newRole{2021 -- 2023}
{Site Reliability Engineer}
{Corpay}

\roleAchievements
{Supported production systems, focusing on incident response, operational automation, and improving developer experience in production environments.}
{Partnered closely with application teams to troubleshoot production issues, improve deployment reliability, and reduce recurring operational pain.}
{Built and refined automation to eliminate manual operational tasks while learning large scale system design and reliability practices from experienced engineers.}
{Contributed to post incident reviews, developing a strong understanding of real world failure modes and system behavior.}
{}{}{}{}{}

\newpage
% -------- DevOps Engineer --------
\newRole{2020 -- 2021}
{DevOps Engineer}
{Flexential}

\roleAchievements
{Designed, automated, and maintained cloud infrastructure across multiple AWS and Azure client environments using Kubernetes, Terraform, and CI/CD pipelines.}
{Served as a technical escalation point for incidents, outages, and complex operational issues across multiple customer environments.}
{Led infrastructure onboarding for new clients and acted as the primary engineer for several production environments.}
{Improved security posture and reliability through infrastructure refactoring, certificate lifecycle management, and proactive incident response.}
{Mentored teammates and collaborated with senior engineers to evolve reference architectures and operational practices.}
{}{}{}{}

\medskip
\begin{center}
\textbf{Remaining work history available on LinkedIn}
\end{center}
\medskip

% =========================
% Projects
% =========================
\newHeading{Projects}

% -------- TradeXSports --------
\newRole{2025 -- Present}
{TradeXSports}
{Client project}

\roleAchievements
{Designed the Azure platform for a client sports product, owning Terraform architecture, Azure DevOps pipelines, release flow, and infrastructure decisions across production and non production environments.}
{Built modular Terraform stacks for Front Door, App Services with deployment slots, private networking, PostgreSQL, Key Vault, VPN access, and Application Insights to support secure delivery and low cost operations.}
{Established CI/CD for infrastructure and application promotion, collaborating with a separate application developer while retaining ownership of platform, deployment, and observability strategy.}
{}{}{}{}{}{}

\medskip

% -------- AWS Queue Jobs --------
\newRole{2025 -- Present}
{Distributed Job Processing Platform}
{Personal project}

\roleAchievements
{Built a distributed job processing platform on AWS using Python, FastAPI, SQS, EKS, Terraform, and\\ Prometheus/Grafana to demonstrate end to end cloud design and operations.}
{Structured infrastructure into foundation, app, compute, and monitoring stacks covering remote state, ECR, OIDC based GitHub Actions access, IRSA, queueing, and managed observability services.}
{Implemented API and worker services with idempotency handling, Prometheus metrics, and queue based processing patterns to show scalable background job execution and operational visibility.}
{}{}{}{}{}{}

\medskip
\begin{center}
\textbf{Additional projects available at \href{https://ericashenden.com}{ericashenden.com} and \href{https://github.com/SuperReliableEric}{github.com/SuperReliableEric}}
\end{center}
\medskip

% =========================
% Education
% =========================
\newHeading{Education}

\newCourse{2012 -- 2016}
{Radford University}
{B.S. Computer Science: Software Engineering}{}

% =========================
% Technical Keywords
% =========================
\newHeading{Technical Keywords}

{\small
\noindent\textbf{Azure:} AKS, App Services, Container Apps, Key Vault, Front Door, Application Gateway, Virtual Networks (VNets),\\
VPN Gateway, Private Endpoints, Managed Identities\\
\textbf{AWS:} EKS, SQS, IAM, ECR\\
\textbf{Containers/Orchestration:} Kubernetes, Helm, KEDA, Docker, Podman\\
\textbf{Infrastructure as Code:} Terraform, Pulumi\\
\textbf{Observability:} Datadog, Prometheus, Grafana, Application Insights\\
\textbf{Languages/Scripting:} PowerShell, Python, Bash\\
\textbf{Data:} SQL (Azure SQL, SQL Managed Instance), PostgreSQL, Cosmos DB, Azure Storage\\
\textbf{CI/CD:} Azure DevOps, GitHub Actions
}

\end{document}
